Enzo: An Adaptive Mesh Refinement Code for Astrophysics

### 2013-01-18 ms.tex
updated ms.tex

% Paper Outline  (last updated June 15, 2009)
%
% 1.  Introduction [GB,MN]
% 2.  Overview [GB]
% - including both equations and a few paragraph overview of how each method works
% - this might have section 2.1, 2.2, etc. corresponding to very brief overviews of section 3.1, 3.2, etc.
% 3.  Numerical methods
%  3.1 AMR [GB]
%  3.2. Hydro: ZEUS [GB]
%  3.3. Hydro: PPM [GB,AK]
%  3.4. Gravity [GB]
%  3.5. Particle Integration [GB]
%  3.6. Chemistry [BWO]
%  3.7. Star formation & Feedback [BWO]
%  3.8. Timestep constraints [BWO,GB]
% 4. Software Implementation
% - maybe this could be split up by into sections 4.1, 4.2, 4.3, etc. using the same scheme as section 3 [same responsibilities as 3]
% 5. Parallelism 
% 5.1. Parallel strategy [GB, RH]
% 5.2. Parallel performance [JB, GB, RH]
% 6. Code Tests [All]
% 7. Summary and Conclusions
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\title{Enzo: An Adaptive Mesh Refinement Code for Astrophysics}
\author{Greg Bryan\altaffilmark{1}, Michael L. Norman\altaffilmark{2}, 
Brian W. O'Shea\altaffilmark{3}, Robert Harkness\altaffilmark{4}, Tom Abel\altaffilmark{5},
David C. Collins,\altaffilmark{2} 
Alexei Kritsuk\altaffilmark{2} and James Bordner\altaffilmark{2} }

\altaffiltext{1}{ Department of Astronomy, Columbia University,
New York, NY, 10027, U.S.A.  Email: gbryan@astro.columbia.edu }
\altaffiltext{2}{Center for Astrophysics and Space Sciences,
University of California at San Diego.
Email: mnorman,dcollins,akritsuk,jbordner@cosmos.ucsd.edu}
\altaffiltext{3}{Theoretical Astrophysics (T-6), Los Alamos National
Laboratories.  Email:  bwoshea@lanl.gov}
\altaffiltext{4}{San Diego Supercomputing Center, University of California
at San Diego.  Email: harkness@sdsc.edu}
\altaffiltext{5}{Kavli Institute for Particle Astrophysics and Cosmology,
 Stanford University.  Email:  tabel@stanford.edu}

@@

\input{numerical-amr}
\input{numerical-ppm}
\input{numerical-zeus}
\input{numerical-gravity}
\input{numerical-particle}
\input{numerical-chemistry}
\input{numerical-starformation}
\input{numerical-timestep}
%\input{numerical-units}

%% Section: software implementation
% \input{software}

@@

%% Section: discussion
\input{discussion}

%% Section: summary
\input{summary}

\appendix

%% Appendix: interpolation
%\input{app-interpolation}

%% Appendix:  Data Structures
\input{app-datastruct}

%% Appendix:  I/O
\input{app-IO}

%% Appendix:  Zeus hydro
%\input{app-zeushydro}

%% Appendix:  PPM hydro
%\input{app-ppmhydro}

%% Appendix:  gravity solver
%\input{app-gravity}

%% Appendix:  
\input{app-chemistry}

>>>>

% Paper Outline  (last updated January 18, 2013)
%
% 1.  Introduction
% 2.  Physical equations and overview
%   2.1 Physical equations
%   2.2 Overview of numerical methods
% 3.  Numerical methods
%   3.1 AMR
%   3.2. Hydro: Godunov (PPM)
%   3.3  Hydro: Godunov (MUSCL)
%   3.4. Hydro: Finite difference (ZEUS)
%   3.5. MHD: Dedner
%   3.6. Gravity
%   3.7. Particle Integration
%   3.8. Chemistry
%   3.9. Cooling
%   3.10. Radiation: Homogeneous
%   3.11  Radiation: ray-tracing
 %  3.12  Radiation: FLD
%   3.13. Star formation & Feedback
%   3.14. Timestep constraints
% 4. Code tests
%   4.1 Verifying and Validating the Enzo code
%   4.2 Representative test problems
% 5. Parallelism 
%   5.1. Parallel strategy 
%   5.2. Parallel performance 
% 6. Code development methodology
% 7. Conclusions
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\title{Enzo: An Adaptive Mesh Refinement Code for Astrophysics}
\author{Authors}

%\altaffiltext{1}{ Department of Astronomy, Columbia University,
%New York, NY, 10027, U.S.A.  Email: gbryan@astro.columbia.edu }
%\altaffiltext{2}{Center for Astrophysics and Space Sciences,
%University of California at San Diego.
%Email: mnorman,dcollins,akritsuk,jbordner@cosmos.ucsd.edu}
%\altaffiltext{3}{Theoretical Astrophysics (T-6), Los Alamos National
%Laboratories.  Email:  bwoshea@lanl.gov}
%\altaffiltext{4}{San Diego Supercomputing Center, University of California
%at San Diego.  Email: harkness@sdsc.edu}
%\altaffiltext{5}{Kavli Institute for Particle Astrophysics and Cosmology,
% Stanford University.  Email:  tabel@stanford.edu}

@@

\input{numerical-amr}
\input{numerical-ppm}
\input{numerical-muscl} % new
\input{numerical-zeus}
\input{numerical-mhd-dedner} % new
\input{numerical-gravity}
\input{numerical-particle}
\input{numerical-chemistry}
\input{numerical-cooling} % new
\input{numerical-radiation-homogeneous} % new
\input{numerical-radiation-raytracing} % new
\input{numerical-radiation-fld} % new
\input{numerical-starformation}
\input{numerical-timestep}
\input{numerical-analysis} % new

@@

%% Section: code development methodology
\input{development} % new

%% Section: conclusions
\input{conclusions}  % new
